---
title: "628Module2"
author: "Yuchen Zeng"
date: "9/28/2019"
output: html_document
---

Adiposity can be compute by weight and height: weight/height^2 unit:公斤 公尺
Use density to predict bodyfat/correct outliers
The 29.50 height => use weight and bmi to recover it
363.1 weight => use height and bmi to recover it
deathlevel bmi max bmi 48.9
don't use the defeault R break when plotting a histogram. Use the number of rows
Check the assumption of linear regression
Use jitter to avoid the overlap of points
R square: best 60-70 good enough and simple model. See how much improvement caused by adding one predictor 
When try to intepret things, try to be user-friendly. If the change is minor in one year, try to intepret it in one decade
Rememebr to do model diagnoise: qqplot, standized residul plot

```{r}
if (!require(ggplot2)){
    install.packages("ggplot2")
    stopifnot(require(ggplot2))
}
if (!require(gridExtra)){
    install.packages("gridExtra")
    stopifnot(require(gridExtra))
}
if (!require(cowplot)){
    install.packages("cowplot")
    stopifnot(require(cowplot))
}
if (!require(olsrr)){
    install.packages("olsrr")
    stopifnot(require(olsrr))
}
if (!require(MASS)){
    install.packages("MASS")
    stopifnot(require(MASS))
}
if (!require(shiny)){
    install.packages("shiny")
    stopifnot(require(shiny))
}
if (!require(shinythemes)){
    install.packages("shinythemes")
    stopifnot(require(shinythemes))
}
if (!require(dplyr)){
    install.packages("dplyr")
    stopifnot(require(dplyr))
}
if (!require(readr)){
    install.packages("readr")
    stopifnot(require(readr))
}
if (!require(rsconnect)){
    install.packages("rsconnect")
    stopifnot(require(rsconnect))
}
```


```{r}
bf = read.csv("BodyFat.csv")
bf
```

```{r}
summary(bf[,-1])
```



```{r}
gp = list()
for (i in 1:15+2){
  my.bf = data.frame(x = bf[,i], y = bf$BODYFAT)
  gp[[i-2]] = ggplot(data=my.bf, aes(x,y)) + geom_point() +
    geom_smooth(method = 'loess') + labs(x = tolower(names(bf)[i]), y = "Body Fat")
}
all_gp = grid.arrange(gp[[1]],gp[[2]],gp[[3]],gp[[4]],gp[[5]],gp[[6]],gp[[7]],
             gp[[8]],gp[[9]],gp[[10]],gp[[11]],gp[[12]],gp[[13]],gp[[14]],gp[[15]],ncol=3,nrow=5)
ggsave("plot1.pdf",all_gp,width = 9, height = 15)
```

By this method, we can delete some potential outliers on prediction bodyfat.

```{r}
lm.density = lm(data=bf, BODYFAT~DENSITY)

outliers = order(abs(lm.density$fitted.values - bf$BODYFAT), decreasing = TRUE)[1:5]
ggplot(data = bf, aes(DENSITY, BODYFAT)) + geom_point(color = "black") + 
  geom_smooth(method = lm) + 
  geom_point(aes(DENSITY[outliers[1]],BODYFAT[outliers[1]]), color = "red") + 
  geom_point(aes(DENSITY[outliers[2]],BODYFAT[outliers[2]]), color = "red") + 
  geom_point(aes(DENSITY[outliers[3]],BODYFAT[outliers[3]]), color = "red") + 
  geom_point(aes(DENSITY[outliers[4]],BODYFAT[outliers[4]]), color = "red") + 
  geom_point(aes(DENSITY[outliers[5]],BODYFAT[outliers[5]]), color = "red") 
```


```{r}
newbf = bf[-outliers,-c(1,3)]
lm.bmi = lm(data = newbf, ADIPOSITY~WEIGHT/HEIGHT^2)
summary(lm.bmi)
residual.order = order(abs(residuals(lm.bmi)), decreasing=TRUE)
qplot(data = newbf, x = WEIGHT/HEIGHT^2, y = ADIPOSITY)
```

```{r}
residual.order = order(abs(residuals(lm.bmi)), decreasing=TRUE)
newbf[residual.order[1],4] = sqrt(newbf[residual.order[1],3]/newbf[residual.order[1],5]*703)
lm.bmi = lm(data = newbf, ADIPOSITY~WEIGHT/HEIGHT^2)
residual.order = order(abs(residuals(lm.bmi)), decreasing=TRUE)
qplot(data = newbf, x = WEIGHT/HEIGHT^2, y = ADIPOSITY)
```

```{r}
newbf = newbf[-residual.order[1:2], ]
row.names(newbf) = 1:dim(newbf)[1]
qplot(data = newbf, x = WEIGHT/HEIGHT^2, y = ADIPOSITY) 
```


```{r}
gp = list()
for (i in 1:14+1){
  my.bf = data.frame(x = newbf[,i], y = newbf$BODYFAT)
  gp[[i-1]] = ggplot(data=my.bf, aes(x,y)) + geom_point() +
    geom_smooth(method = 'loess') + labs(x = tolower(names(newbf)[i]), y = "Body Fat")
}
all_gp = grid.arrange(gp[[1]],gp[[2]],gp[[3]],gp[[4]],gp[[5]],gp[[6]],gp[[7]],
             gp[[8]],gp[[9]],gp[[10]],gp[[11]],gp[[12]],gp[[13]],gp[[14]],ncol=3,nrow=5)
ggsave("plot2.pdf",all_gp,width = 30, height = 50, limitsize = FALSE)
```

The relationship between adiposity and weight and height.

```{r}
lm.full = lm(data = newbf, BODYFAT~.)
model.aic.both <- step(lm.full, direction = "both", k = 2)
summary(model.aic.both)
```


```{r}
step.result = ols_step_all_possible(lm.full)
```

```{r}
write.csv(step.result, "step_result.csv")
```


```{r}
lm.final = lm(data=newbf, BODYFAT~WEIGHT+ABDOMEN)
summary(lm.final)
plot(lm.final)
qplot(data = newbf, x = lm.final$coefficients[2]*WEIGHT+lm.final$coefficients[3]*ABDOMEN, y = BODYFAT)+geom_smooth()
```

```{r}
n=dim(newbf)[1];p=2;index = 1:n
#leverage
h<-2*p/n
le<-hatvalues(lm.final)
qplot(index, le)+labs(y="Leverage", x="Index")+
   geom_abline(aes(intercept=h,slope=0),colour="blue")+
      annotate(geom = "text", x = index, y = le, label = index)+
        geom_linerange(x=index, ymin=0, ymax=le)
#diffits
h<-2*sqrt(p/n)
dfs<-dffits(lm.final)
qplot(index, dfs)+labs(y="DFFITS", x="Index")+
   geom_abline(aes(intercept=-h,slope=0),colour="blue", linetype="dashed")+
      geom_abline(aes(intercept=h,slope=0),colour="blue", linetype="dashed")+
        geom_abline(aes(intercept=-1,slope=0),colour="blue", linetype="dashed")+
          geom_abline(aes(intercept=1,slope=0),colour="blue", linetype="dashed")+
            annotate(geom = "text", x = index, y = dfs, label = index)+
              geom_linerange(x=index, ymin=0, ymax=dfs)+
                geom_abline(aes(intercept=0,slope=0),colour="blue")
#cook's distance
h<-qf(0.50,p,n-p)
cd<-cooks.distance(lm.final)
qplot(index, cd)+labs(y="Cook's Distance", x="Index")+
   geom_abline(aes(intercept=h,slope=0),colour="blue")+
      annotate(geom = "text", x = index, y = cd, label = index)+
        geom_linerange(x=index, ymin=0, ymax=cd)
```

```{r}
newbf = newbf[-39,]
row.names(newbf) = 1:dim(newbf)[1]
```

```{r}
lm.final2 = lm(data=newbf, BODYFAT~WEIGHT+ABDOMEN)
summary(lm.final2)
qplot(data = newbf, x = lm.final2$coefficients[2]*WEIGHT+lm.final2$coefficients[3]*ABDOMEN, y = BODYFAT)+geom_smooth()
```

```{r}
plot(lm.final2)
shapiro.test(studres(lm.final2))
```

```{r}
bc = boxcox(lm.final2)
lambda <- bc$x[which(bc$y==max(bc$y))]
lm.final3 = lm(data=newbf, BODYFAT^lambda~WEIGHT+ABDOMEN)
summary(lm.final3)
```

```{r}
plot(lm.final3)
ks.test(studres(lm.final3))

```

```{r}
ui <- fluidPage(
  titlePanel("BodyFat Calculator"),

  sidebarLayout(
    sidebarPanel("Calculator",
    numericInput("weight",h3("Weight (lbs)"), value = 1),
    numericInput("abodmen",h3("The circumference of abodmen (cm)"), value = 1)),
    mainPanel(h1("Confidence Intervel of your bodyfat"),
              textOutput(outputId = "bodyfat")
              )
  )
)

server <- function(input,output) {
  output$bodyfat = renderText({
  paste0("You bodyfat is: ", 
         predict(lm.final3, newdata = data.frame(WEIGHT = input$weight, ABDOMEN=input$abodmen), interval = "predict")[1],".\n","The 95% confidence interval of your bodyfat is", "[", 
         predict(lm.final3, newdata = data.frame(WEIGHT = input$weight, ABDOMEN=input$abodmen), interval = "predict")[2],",", 
         predict(lm.final3, newdata = data.frame(WEIGHT = input$weight, ABDOMEN=input$abodmen), interval = "predict")[3], "].")}
  )
  
}

shinyApp(ui = ui, server = server)


```

